\documentclass[11pt]{moderncv}
\usepackage[authoryear]{natbib}

\DeclareOldFontCommand{\rm}{\normalfont\rmfamily}{\mathrm}
\DeclareOldFontCommand{\sf}{\normalfont\sffamily}{\mathsf}
\DeclareOldFontCommand{\tt}{\normalfont\ttfamily}{\mathtt}
\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
\DeclareOldFontCommand{\it}{\normalfont\itshape}{\mathit}
\DeclareOldFontCommand{\sl}{\normalfont\slshape}{\@nomath\sl}
\DeclareOldFontCommand{\sc}{\normalfont\scshape}{\@nomath\sc}
\DeclareRobustCommand*\cal{\@fontswitch\relax\mathcal}
\DeclareRobustCommand*\mit{\@fontswitch\relax\mathnormal}

\moderncvtheme[blue]{classic}

\usepackage[scale=0.8]{geometry}

\firstname{Antonio}
\familyname{{}Linero}
\title{Assistant Professor of Statistics}
\address{Tallahassee}{Florida}
\email{arlinero@stat.fsu.edu}
\homepage{ani.stat.fsu.edu/\textasciitilde arlinero}
\extrainfo{\today}

% Define \cvdoublecolumn, which sets its arguments in two columns
% without any labels

\newcommand{\cvdoublecolumn}[2]{%
  {}{%
    \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#1\end{minipage}%
    \hfill%
    \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#2\end{minipage}%
   }%
}

% usage: \cvreference{name}{address line 1}{address line 2}{address
% line 3}{address line 4}{e-mail address}{phone number} Everything but
% the name is optional If \addresssymbol, \emailsymbol or \phonesymbol
% are specified, they will be used.  (Per default, \addresssymbol
% isn't specified, the other two are specified.)  If you don't like
% the symbols, remove them from the following code, including the
% tilde ~ (space).

\newcommand{\cvreference}[7]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7}}

\setlength{\hintscolumnwidth}{0.2\textwidth}

% \cventry{year–year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}

\begin{document}
\maketitle

\section{Professional Experience}

\cventry{August 2015--Present}{Assistant Professor}{Florida State University}
        {Department of Statistics}{}{}

\section{Education}

\cventry{2010--2015}{PhD, Statistics}{University of
  Florida}{}{}{{Dissertation ---  {\em Nonparametric Bayes: Inference Under
  Nonignorable Missingness and Model Selection}}}

\cventry{2005--2009}{BS, Finance}{University of Florida}{}{}{Minor---Statistics}

% \cvitem{}{}

\section{External Funding}


\cvitem{2018--2022}{\emph{The Science of Test} (Co-PI). Funded by
  Department of Defense (extension of SOT-FSU-FATs-16-06). Total award \$478,000.}{}

\cvitem{2017--2020}{\emph{Leveraging Structural Information in Decision Tree
    Ensembles} (PI). Funded by the National Science Foundation (NSF-DMS
  1712870). Total award \$100,000.}{}

\cvitem{2016--2018}{\emph{Functional Analysis Tools} (Co-PI). Funded by
  Department of Defense (SOT-FSU-FATs-16-06). Total award \$176,000.}{}



\section{Awards}

\cventry{Spring 2016}{First Year Assistant Professor Award}{Florida State University}
{}{}{Funding for summer research work.}

\cventry{Spring 2015}{CLAS Dissertation Fellowship}{University of
  Florida}{}{}{Funding for writing of PhD dissertation.}

\cventry{2014}{Statistics Faculty Award}{University of
  Florida}{}{}{Awarded to ``the best graduating PhD student'' in the
  Department of Statistics.}

\cventry{2014}{Laplace Award}{}{}{awarded by the International Society
  for Bayesian Analysis and the Section of Bayesian Statistical
  Science of the American Statistical Association}{For best Bayesian
  student paper.} 


\section{Publications in review}

\cvitem{}{Varbanov, R., Chicken, E., \textbf{Linero, A.R.}, and Yang, Y. (2018)
  A Bayesian Approach to Sequential Monitoring of Nonlinear Profiles Using Wavelets. Submitted.}

\cvitem{}{\textbf{Linero, A.R.} and Yang, Y. (2017) Bayesian Regression Tree Ensembles that Adapt to Smoothness and Sparsity. Major revision requested by \emph{Journal of the Royal Statistical Association, Series B.}}

\section{Publications in press}


\cvitem{}{\textbf{Linero, A.R.} and Daniels, M.J. (2018)  Bayesian Approaches for Missing Not at Random Outcome Data: The Role of Identifying Restrictions.
  \emph{Statistical Science,} \textbf{33}(2), 198--213.}


\cvitem{}{\textbf{Linero, A.R.} (2018) Bayesian regression trees for high
  dimensional prediction and variable selection. \emph{Journal of the American
    Statistical Association.}}

\cvitem{}{\textbf{Linero, A.R.} and Bradley, J.R (2017) Multi-rubric Models for
  Ordinal Spatial Data with Application to Online Ratings. \emph{Annals of Applied Statistics.} To appear.}

\cvitem{}{\textbf{Linero, A.R.} (2017) A Review of Tree-Based Bayesian Methods. \emph{Communications for Statistical Applications and Methods,} \textbf{24}(6), 543--559.}

\cvitem{}{Varbanov, R., Chicken, E., and \textbf{Linero, A.R.} (2017)
  Wavelet-Based Bayesian Profile Monitoring. \emph{Proceedings of
    the 2017 Industrial and Systems Engineering Research Conference.}}

\cvitem{}{\textbf{Linero, A.R.} (2017) Bayesian Nonparametric Analysis of
  Longitudinal Studies in the Presence of Informative Missingness.
  \emph{Biometrika,} \textbf{104}(2), 371--341}


\cvitem{}{
  Piekarewicz, J., \textbf{Linero, A.R.}, Giuliani, P., and Chicken, E. (2016)
  The power of two: Assessing the impact of a second measurement of the weak-charge
  form factor of \(^{208}\textnormal{Pb}\). \emph{Physical Reviews C,}
  \textbf{94}(3), 034316.
}

\cvitem{}{Daniels, M.J. and {\bf Linero, A.R.} (2015) Bayesian
  nonparametrics for missing data in longitudinal clinical
  trials. In {\em Nonparametric Bayesian Inference in Biostatistics.}}

\cvitem{}{{\bf Linero, A.R.} and Daniels, M.J. (2015) A flexible
  Bayesian approach to monotone missing data in longitudinal studies
  with nonignorable missingness with application to an acute
  schizophrenia clinical trial. {\em Journal of the American
    Statistical Association,} {\bf 110}(509), 45--55.}

\cvitem{}{{\bf Linero, A.R} and Rosalsky, A. (2013) On the Toeplitz
  lemma, convergence in probability, and mean convergence. {\em Stochastic
  Analysis and Applications,} {\bf 31}(4), 684-694.}
  

% \nocite{*}
% \bibliographystyle{unsrt}
% \bibliographystyle{apalike}
% \bibliographystyle{unsrtnat}
% \bibliography{publications}


% \section{Manuscripts in Preparation}

% \cvitem{}{Bradley, J.R., \textbf{Linero, A.R.} and Chicken, E.K. A
%   repeated--measures multivariate spatio--temporal mixed effects model for
%   ordinal data.}

% \cvitem{}{{\bf Linero, A.R.} and Doss, H. A Fully-Bayes Approach to Empirical
%   Bayes Inference and Bayesian Sensitivity Analysis.}

% \section{Invited Presentations}

% \cvitem{01/12/2015}{Flexible Bayesian Analysis in the Presence of
%   Nonignorable Missingness. {\em Florida State University}}
% \cvitem{01/20/2015}{Flexible Bayesian Analysis in the Presence of
%   Nonignorable Missingness. {\em Arizona State University}}
% \cvitem{01/29/2015}{Flexible Bayesian Analysis in the Presence of
%   Nonignorable Missingness. {\em University of Illinois at Urbana Champaign}}
% \cvitem{02/08/2015}{Flexible Bayesian Analysis in the Presence of
%   Nonignorable Missingness. {\em Texas A\&M University}}


\section{Service}

\cventry{2018 -- 2020}{Associate Editor}{}{}{Biometrics}{}

\cventry{}{Referee}{}{}{
  Annals of Applied Statistics,
  Biometrics,
  Biometrika, 
  Journal of the American Statistical Association,
  Journal of Computational and Graphical Statistics,
  Journal of Epidemiology,
  Journal of the Korean Statistical Society,
  Journal of Statistical Distributions and Applications,
  PLOS One,
  Psychological Methods,
  Sankhya Series A,
  Statistica Sinica,
  Statistical Methods in Medical Research,
  Statistical Science,
  Statistics in Medicine
}{} 

% \cventry{2016}{CM Statistics}{}{}{Chair of session ``Bayesian Methods for
%   Dependent Data''}{}

% \cventry{2014}{ENAR Spring Meeting}{}{}{Chair of session ``Innovative
%   Bayesian Nonparametrics in Biostatistics''}{}

\section{Teaching}

\cvitem{\textbf{STA4442}}{Introduction to Probability. Fall 2015, Spring 2017, 2018}
\cvitem{\textbf{STA5168}}{Statistics in Applications 3. Fall 2016, 2017, 2018}
\cvitem{\textbf{STA3032}}{Engineering Statistics. Spring 2016}




% \section{Research Interests}

% \cvitem{}{Applications of Bayesian methods to problems in
%   Biostatistics and machine learning.}  

% \cvitem{}{Inference in longitudinal studies with
%   missing data and causal inference.}

% \cvitem{}{Bayesian nonparametrics and semiparametrics.}

% \cvitem{}{Computational issues associated with the above.}

%\section{References}
%
%\cvdoublecolumn{
%  \cvreference{Michael Daniels}
%  {Section of Integrative Biology, Department of Statistics \& Data Sciences}
%  {University of Texas at Austin}
%  {Austin, TX}
%  {}
%  {mjdaniels@austin.utexas.edu}
%  {512-471-4128}
%  \\[1em] \ \\
%  \cvreference{Malay Ghosh}
%  {Department of Statistics}
%  {University of Florida}
%  {}
%  {Gainesville, Florida}
%  {ghoshm@stat.ufl.edu}
%  {352-273-2992}
%  \\[1em] \ \\
%  \cvreference{Nikolay Bliznyuk}
%  {Institute of Food and Agricultural Sciences, Statistics Unit}
%  {University of Florida} 
%  {}
%  {Gainesville, Florida}
%  {nbliznyuk@ufl.edu}
%  {352-392-1946}
%}
%{\cvreference{Hani Doss}
%  {Department of Statistics}
%  {University of Florida}
%  {}
%  {Gainesville, Florida}
%  {doss@stat.ufl.edu }
%  {352-273-2991 }
%  \\ \ \\ \ \\ \ \\ \
%  \cvreference{Andrew Rosalsky}
%  {Department of Statistics}
%  {University of Florida}
%  {Gainesville, Florida}
%  {}
%  {rosalsky@stat.ufl.edu}
%  {352-273-2983}
%}

\end{document}

%  LocalWords:  Statistica Sinica
